SemanticPaint

### 2015-12-05 cv3d_seminar/paper.tex
add references and abstract

\begin{abstract}
	The short abstract (50-80 words) is intended to give the reader an overview of the work.
\end{abstract}

@@

  Capturing your own environment has never been easier. SemanticPaint can register your surroundings which, after 3D reconstruction, can be semantically segmented in an interactive way. Not only it works in real time but also requires no pretraining. Adding new object categories on the fly is facilitated by online model updates. The user is provided with instantaneous feedback and can re-label any object to correct errors. SemanticPaint makes capturing customized environment models with object classes particular to the user's interest easy and efficient.

@@

  \bibitem{htree}
  DOMINGOS , P. AND HULTEN , G. 2000. Mining high-speed data streams. In Proc. SIGKDD.

@@

>>>>

\begin{abstract}
  We describe SemanticPaint \cite{SemanticPaint} --- a system for capturing and  interactive segmentation of 3D enviornments. It allows adding new object categories at runtime, updates the model with and infers labels of newly seen data in an online fashion. 
\end{abstract}

@@

  Capturing your own environment has never been easier. SemanticPaint \cite{SemanticPaint} register your surroundings which, after 3D reconstruction, can be semantically segmented in an interactive way. Not only it works in real time but also requires no pretraining. Adding new object categories on the fly is facilitated by online model updates. The user is provided with instantaneous feedback and can re-label any object to correct errors. SemanticPaint makes capturing customized environment models with object classes particular to the user's interest easy and efficient.

@@

  \bibitem{htree}
  DOMINGOS, P. AND HULTEN , G. 2000. Mining high-speed data streams. In Proc. SIGKDD.

@@

  \bibitem{SemanticPaint}
  VALENTIN, J., VINEET, V., CHENG, M.-M., KIM, D., SHOTTON, J., KOHLI, P., NIESSNER, M., CRIMINISI, A., IZADI, S., TORR, P. 2015. SemanticPaint: Interactive 3D Labeling and Learning at your Fingertips. SIGGRAPH.
